---
title: "Rose_fproject"
author: "Rosemary Madaki"
format: html
editor: visual
theme: pulse
execute: 
  eval: true
  echo: false
---

## Background

This is a brief report on a research conducted on assessing the relationship between salt consumption and blood pressure among 12 students. This data was graciously donated by the Department of Biostatistics, Ahmadu Bello University, Zaria.

## Results

```{r}
#| echo: false
#| message: false
library(tidyverse)
library(gtsummary)
library(ggplot2)
library(readr)
library(dplyr)

#Loading my dataset
#Step2 loading my A NEW dataset, the step below worked
sosonew <- read_csv(here::here("mdata", "sosonew.csv"))




```

```{r}
#| label: tbl-descr
#| tbl-cap: "Descriptive Statistics of Data"
table1<-tbl_summary(
	sosonew,
	by = Sex,
	include = c(BP, Site),
	label = list(
		BP ~ "Blood Pressure",
		Site ~ "Location"
	),
	missing_text = "Missing")
table1

inline_text(table1, variable = "Site", level = "BRK",
                         column = "M")
inline_text(table1, variable = "Site", level = "ATL",
                         column = "M")


male_b<-inline_text(table1, variable = "Site", level = "BRK",
                         column = "M")
male_a<-inline_text(table1, variable = "Site", level = "ATL",
                         column = "M")
#| message: false
```

@tbl-descr is a table. As seen above, there were more males in Brooklyn (`r male_b`) than Atlanta (`r male_a`) .

```{r}
#| label: tbl-two
#| tbl-cap: "Linear Regression of Data"
table2<-tbl_uvregression(
	sosonew,
	y = Sodium,
	include = c(BP, Patient,
							Sex, Site),
	method = lm)
table2

```

@tbl-two is a table showing some regression analysis.

```{r}
#| label: fig-hist
#| fig-cap: "This is a histogram"
fig1<-ggplot(data = sosonew, aes(x = BP)) +
	geom_histogram(binwidth = 20)
fig1


```

@fig-hist is a histogram displaying the range of blood pressure.

## Conclusion
The analysis revealed a significant association between sex and blood pressure.



