---
title: "Rose_fproject"
author: "Rosemary Madaki"
format: html
editor: visual
theme: flatly
---

## Background

This is a brief report on a research conducted on assessing the relationship between salt consumption and blood pressure. This data was graciously donated by the Department of Biostatistics, Ahmadu Bello University, Zaria.

## Results

```{r}
#| echo: false
#| message: false
library(tidyverse)
library(gtsummary)
#Loading my dataset
#Step2 loading my A NEW dataset, the step below worked
sosonew <- read_csv(here::here("mdata", "sosonew.csv"))

```

```{r}
#| label: tbl-descr
#| tbl-cap: "Descriptive Statistics of Data"
table1<-tbl_summary(
	sosonew,
	by = Sex,
	include = c(BP, Site),
	label = list(
		BP ~ "Blood Pressure",
		Site ~ "Location"
	),
	missing_text = "Missing")
table1
#sample code

#my code
inline_text(table1, variable = "Site", level = "BRK",
                         column = "M")
inline_text(table1, variable = "Site", level = "ATL",
                         column = "M")
#creating a factor to be referred to

male_b<-inline_text(table1, variable = "Site", level = "BRK",
                         column = "M")
male_a<-inline_text(table1, variable = "Site", level = "ATL",
                         column = "M")
```
@tbl-descr is a table. As seen above, there were more males in Brooklyn (`r male_b`) than Atlanta (`r male_a`) .

Improve the next chunk for the regression table
```{r}
#| label: tbl-two
#| tbl-cap: "Linear Regression of Data"
table2<-tbl_uvregression(
	sosonew,
	y = Sodium,
	include = c(BP, Patient,
							Sex, Site),
	method = lm)
table2
```
@tbl-two is a table showing some summary statistics.


When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false

2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

Some more chunks

```{r}
2+5
```

MORE CHUNKS

```{r}
#| echo: false
#| eval: true
3
```
